What do incoming university students believe about open science practices in

### 2021-10-29 analysis/Manuscript.Rmd
update code for abstract
update comments re abstract
minor change to wording in norms in practice

<!--
Teaching in Psychology ask for structured abstracts - 'For these types of article submissions, please include (in this order) a section on the background, objective(s), method, results, conclusion, and teaching implications.' 200 word limit
Abstract currently includes hand-typed numbers because it's hard to get them to knit up here since data processing is further below.
The abstract also doesn't currently knit into the final document for some reason?
JB: I tried to fix this too and looked at all sorts of troubleshooting guides, but no luck.

-->

@@

To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies. J
B: Yes, that's a good note to include for folks.
-->

@@

# need to figure out whether I can rotate a page in papaja
# EK - You can rotate the table, but I don't think it will rotate the page and it won't
# carry over into word. 
# JB: Moving correlations to a supplement will sove the problem I'm trying to resolve anyway...

@@

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

>>>>

<!--
Teaching in Psychology ask for structured abstracts - 'For these types of article submissions, please include (in this order) a section on the background, objective(s), method, results, conclusion, and teaching implications.' 200 word limit
Abstract currently includes hand-typed numbers because it's hard to get them to knit up here since data processing is further below.
-->

@@

To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies. 
JB: Yes, that's a good note to include for folks.
-->

@@

# need to figure out whether I can rotate a page in papaja
# EK - You can rotate the table, but I don't think it will rotate the page and it won't
# carry over into word. 
# JB: Moving correlations to a supplement will solve the problem I'm trying to resolve anyway...

@@

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. See Figure A in Supplemental Materials to see the distribution for each item. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
